### 2023-06-29 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
worked on lubrication layer size plot

\begin{figure}[h]
    \centering
    \subfigimg[width = \columnwidth]{(a)}{figures/Fig8a.pdf}\\
    \subfigimg[width = \columnwidth]{(b)}{figures/Fig8b.pdf}
    \caption{\small Lubrication layer of a single-component and a multicomponent vesicle moving through a stenosed channel. In the top figure, the reduced area is 0.4, on the bottom it is 0.6.}
    \label{fig:lubrication}
\end{figure}

>>>>

\begin{figure}[h]
    \centering
    \subfigimg[width = 0.49\columnwidth]{(a)}{figures/Layer_Size_RAp4.pdf}
    \subfigimg[width = 0.49\columnwidth]{(b)}{figures/Layer_Size_RAp6.pdf}
%    \subfigimg[width = \columnwidth]{(a)}{figures/Fig8a.pdf}\\
%    \subfigimg[width = \columnwidth]{(b)}{figures/Fig8b.pdf}
    \caption{\label{fig:lubrication} \small The size of the lubrication
    layer of a stiff single component (red), floppy single component
    (green), and multicomponent (blue) vesicle passing through stenosis.
    Solid lines are the layer thickness between the vesicle and the top
    wall, and dashed lines are the layer thickness between the vesicle
    and the bottom wall. The reduced area of the vesicles are (a)
    $\alpha = 0.4$ and (b) $\alpha = 0.6$.}
\end{figure}
